|

### 2023-08-26 appendix/appendix.Rmd
change table seven appendix

---
title: |
       | Supplemental Materials for "Legislature Size and Welfare: Evidence from Brazil"
author: 
  - Umberto Mignozzetti[^umberto]
  - Gabriel Cepaluni[^gabriel]
  - Danilo Freire[^danilo]
date: August 26, 2022
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

Table \ref{accurClassif} shows the classification accuracy for each of the variables that we have hand-coded. In all models, we set cost to 10 to avoid overfitting.

\begin{table}[htb!]
\centering
\caption{Accuracy of SVM Classifier (Tested in 20\% of the Data)}
\label{accurClassif}
\begin{tabular}{lc}
\hline
\textbf{Variable}            & \textbf{Accuracy}  \\
\hline
Local Public Goods           & 93.8               \\
Oversight                    & 94.9               \\
Education and Health Care    & 92.5               \\
Others                       & 93.5               \\
\hline
\end{tabular}
\end{table}

>>>>

---
title: |
       | Supplemental Materials for "Legislature Size and Welfare: Evidence from Brazil"
author: 
  - Umberto Mignozzetti[^umberto]
  - Gabriel Cepaluni[^gabriel]
  - Danilo Freire[^danilo]
date: ""
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@
